Modern Graph Generators: A Survey

### 2018-10-19 comparison.tex
Modification of tables (community detection)

At first we classify the generators on the basis of the respective application domains or user communities. In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, (5) graph analytics, and (6) graph data steaming. The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas. Thus we believe that they form a natural first acquaintance for the reader.

In Table~\ref{tab:comparisonCharacteristics}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``An.'' stands for graph analytics, ``St.'' stands for graph streaming. Value ``$-$'' means that the information is not available or relevant.} In particular, we show:

@@

\multirow{7}{*}{\rot{\textbf{General}}}

@@

  & Graph 500  & -- & -- & Y & N & Y & power-law & edge-list &  Y  \\

@@

\multirow{2}{*}{\rot{\textbf{An.}}}

@@

@@

  & Graphalytics & extracted & social network & fixed& N& N & power-law & CSV, RDF & N   \\

@@

\multirow{2}{*}{\rot{\textbf{St.}}}

@@

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & \cite{Barabasi99emergenceScaling} & {\bf x} & & & & x & \\
\cline{2-8}
   & R-MAT    & {\bf x} & & & & x & \\
\cline{2-8}
  & GraphGen  & {\bf x} & & x & & & \\
\cline{2-8}
  & Graph 500 & {\bf x} & & & & x & \\
\cline{2-8}
  & BTER      & {\bf x} & & & & & \\
\cline{2-8}
  & Darwini   & {\bf x} & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & & & & \\
\cline{2-8}
 & LBBM  & & {\bf x} & & & & \\
\cline{2-8}
 & UOBM  & & {\bf x} & & & & \\
\cline{2-8}
 & IIMB & & {\bf x} & & & & \\
\cline{2-8}
 & BSBM & & {\bf x} & & & & \\
\cline{2-8}
 & SP$^2$Bench & & {\bf x} & & & & \\
\cline{2-8}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & \\
\cline{2-8}
 & DBPSB & & {\bf x} & & & & \\
\cline{2-8}
 & LODIB & & {\bf x} & & & & \\
\cline{2-8}
 & SIB & & {\bf x} & & & & \\
\cline{2-8}
 & Geographica & & {\bf x} & & & & \\
\cline{2-8}
 & WatDiv & & {\bf x} & & & & \\
\cline{2-8}
 & RBench & & {\bf x} & & & & \\
\cline{2-8}
 & LDBC SPB & & {\bf x} & & & & \\
\cline{2-8}
 & LinkGen & & {\bf x} & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x & & \\
\cline{2-8}
  & gMark & & x & {\bf x} & x & & \\
\cline{2-8}
  & graphGen & & & {\bf x} & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & \\
\cline{2-8}
 & \cite{Yao2011}  & & & & {\bf x} & & \\
\cline{2-8}
 & LinkBench  & & & x & {\bf x} & & \\
\cline{2-8}
 & S3G2  & & x & x & {\bf x} & & \\
\cline{2-8}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & \\
\cline{2-8}
 & LDBC SNB   & & x & x & {\bf x} & & \\
\cline{2-8}
  & \cite{Nettleton2016}  & & & & {\bf x} & & \\
\hline
\hline   % ======================   graph analytics
\multirow{2}{*}{\rot{\textbf{An.}}}
  & HPC Scal. Graph Anal.  & & & & & {\bf x} & \\
\cline{2-8}
  & Graphalytics & & & & & {\bf x} & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & & & & & & {\bf x}\\
\cline{2-8}
  & RSPLab & & & & & & {\bf x} \\
%\cline{2-8}
%  & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

For example, many general or domain-agnostic graph generators such as the
preferential attachment~\cite{Barabasi99emergenceScaling}, R-MAT or Graph 500, are typically used to test graph
analytics frameworks when large real graphs are not available. Actually,
Graphalytics uses R-MAT as one as its graph generators for benchmarking graph
analytics.

>>>>

At first we classify the generators on the basis of the respective application domains or user communities. In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, (5) graph analytics, (6) community detection, and (7) graph data steaming. The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas. Thus we believe that they form a natural first acquaintance for the reader.

In Table~\ref{tab:comparisonCharacteristics}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``A'' stands for graph analytics, ``Co'' stands for community detection, and ``St'' stands for graph streaming. Value ``$-$'' means that the information is not available or relevant.} In particular, we show:

@@

\multirow{6}{*}{\rot{\textbf{General}}}

@@

%  & Graph 500  & -- & -- & Y & N & Y & power-law & edge-list &  Y  \\

@@

\multirow{1}{*}{\rot{\textbf{A}}}

@@

%  & Graphalytics & extracted & social network & fixed& N& N & power-law & CSV, RDF & N   \\
\hline   %  ======================  community detection
\multirow{2}{*}{\rot{\textbf{Co}}}
  &  &  &  &  &  &  &  &  &      \\

@@

  &  &  & &  &  &  & &  &      \\

@@

\multirow{2}{*}{\rot{\textbf{St}}}

@@

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Community detection}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{5}{*}{\rot{\textbf{General}}}
  & \cite{Barabasi99emergenceScaling} & {\bf x} & & & & x & & \\
\cline{2-9}
   & R-MAT    & {\bf x} & & & & x & & \\
\cline{2-9}
  & GraphGen  & {\bf x} & & x & & & & \\
\cline{2-9}
%  & Graph 500 & {\bf x} & & & & x & & \\
%\cline{2-9}
  & BTER      & {\bf x} & & & & & & \\
\cline{2-9}
  & Darwini   & {\bf x} & & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & LBBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & UOBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & IIMB & & {\bf x} & & & & & \\
\cline{2-9}
 & BSBM & & {\bf x} & & & & & \\
\cline{2-9}
 & SP$^2$Bench & & {\bf x} & & & & & \\
\cline{2-9}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & & \\
\cline{2-9}
 & DBPSB & & {\bf x} & & & & & \\
\cline{2-9}
 & LODIB & & {\bf x} & & & & & \\
\cline{2-9}
 & SIB & & {\bf x} & & & & & \\
\cline{2-9}
 & Geographica & & {\bf x} & & & & & \\
\cline{2-9}
 & WatDiv & & {\bf x} & & & & & \\
\cline{2-9}
 & RBench & & {\bf x} & & & & & \\
\cline{2-9}
 & LDBC SPB & & {\bf x} & & & & & \\
\cline{2-9}
 & LinkGen & & {\bf x} & & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x & & & \\
\cline{2-9}
  & gMark & & x & {\bf x} & x & & & \\
\cline{2-9}
  & graphGen & & & {\bf x} & & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & & \\
\cline{2-9}
 & \cite{Yao2011}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LinkBench  & & & x & {\bf x} & & & \\
\cline{2-9}
 & S3G2  & & x & x & {\bf x} & & & \\
\cline{2-9}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LDBC SNB   & & x & x & {\bf x} & & & \\
\cline{2-9}
  & \cite{Nettleton2016}  & & & & {\bf x} & & & \\
\hline
\hline   % ======================   graph analytics
\multirow{1}{*}{\rot{\textbf{A}}}
  & HPC Scal. Graph Anal.  & & & & & {\bf x} & & \\
%\cline{2-9}
%  & Graphalytics & & & & & {\bf x} & & \\
\hline
\hline   %  ======================  community detection
\multirow{2}{*}{\rot{\textbf{Co}}}
  &  & & & & & & {\bf x} &\\
\cline{2-9}
  &  & & & & & & {\bf x} & \\
%\cline{2-9}
%  & & & & & & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St}}}
  & S2Gen & & & & & & & {\bf x}\\
\cline{2-9}
  & RSPLab & & & & & & & {\bf x} \\
%\cline{2-9}
%  & & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

For example, many general or domain-agnostic graph generators, such as the
preferential attachment~\cite{Barabasi99emergenceScaling} or R-MAT, are typically used to test graph
analytics frameworks when large real graphs are not available. Actually,
Graphalytics uses R-MAT as one as its graph generators for benchmarking graph
analytics.
